Gender and Mental Depression: Analyzing Census Data Through Statistical Methods

### 2024-10-25 paper/paper.qmd
Abstract fixed

---
title: "Gender and Mental Depression: Analyzing Census Data Through Statistical Methods"
author: 
  - Christina Nguyen
  - Marcus Barnes
  - Nibras Ar Rakib
thanks: "Code and data are available at: [https://github.com/Nguyen-Ar-Rakib-Barnes/downturns-household-insurance-and-poverty](https://github.com/Nguyen-Ar-Rakib-Barnes/downturns-household-insurance-and-poverty)."
date: today
date-format: long
abstract: "Mental health poses a significant global health threat. This threat existed before the pandemic, and recent studies have shown that it has become even more prevalent after the pandemic. Our study developed a method to identify severe psychological depression using survey data that can be used as an early alert system to identify nonspecific psychological distress."
format: pdf
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "Gender and Mental Depression: Analyzing Census Data Through Statistical Methods"
author: 
  - Christina Nguyen
  - Marcus Barnes
  - Nibras Ar Rakib
thanks: "Code and data are available at: [https://github.com/Nguyen-Ar-Rakib-Barnes/downturns-household-insurance-and-poverty](https://github.com/Nguyen-Ar-Rakib-Barnes/downturns-household-insurance-and-poverty)."
date: today
date-format: long
abstract: "Mental health posed a significant global health threat before the pandemic, and recent studies have shown that it has become even more prevalent. Our study developed a method to identify severe psychological depression using survey data that can be used as an early alert system to identify nonspecific psychological distress."
format: pdf
number-sections: true
bibliography: references.bib
---
